---
title: "Getting Started with binomial"
author: "Yeqing Chen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to cointoss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
library(ggplot2)
```

# Introduction to binomial

The Binomial distribution is perhaps the most famous probability distribution among discrete
random variables. This is the theoretical probability model that we use when calculating
probabilities about the number of successes in a fixed number of random trials performed
under identical conditions (assuming a constant probability of success on each trial).

The formula of the binomial probability:


$P_r(X = k) =({^n_k})p^k(1-p)^{n-k}$

where:
- n is the number of (fixed) trials $(n \geqslant 0)$

- p is the probability of success on each trial $(0 \leqslant p \leqslant 1)$

- 1-p is the probability of failure on each trial

- k is a variable that represents the number of successes out of n trials $(0\leqslant k \leqslant n)$

- the first term in parenthesis is NOT a fraction, it is the number of combinations in which k success can occur in n trials

This document introduces you to binomial's basic set of tools, and shows you how to apply them to calculate binomial distribution.

## 1. Calculates the number of combinations in which k successes can occur in n trials.


for example, finding the number of combination in getting 3 heads in 4 tosses.

```{r}
bin_choose(n=4,k=3)
```

## 2. Calculates the probability in whick k successes can occur in n trials with a constant probability of success on each trial.


for example, finding the probability of getting 3 heads in 4 tosses of a fair coin.

```{r}
bin_probability(success = 3,trials = 4,prob = 0.5)
```


## 3. obtain a data with the probability distribution.

for example, the probability distribution for 4 tosses of a fair coin

```{r}
dis1 <- bin_distribution(trials = 4, prob = 0.5)
dis1
```


Note: sucesses in the first column, probability in the second column.


### 3.1 Plot the histogram of the probability distribution

```{r}
plot(dis1)
```

## 4 obtain a data with the cumulative probability distribution.

for example, the cumulative probability distribution for 4 tosses of a fair coin.

```{r}
dis2 <- bin_cumulative(4,0.5)
dis2
```


### 4.1 Plot the cumulative probability distribution

```{r}
plot(dis2)
```


## 5. list with named elements for binomial variables

for example, the binomial distribution for 4 tosses of a fair coin

```{r}
bin1 <- bin_variable(trials = 4, prob = 0.5)
bin1
```


### 5.1 list with named elements and summary for binomial variables


```{r}
binsum1 <- summary(bin1)
binsum1
```

## 6 Calculate measures of binomial distribution

for example, the binomial distribution for 4 tosses of a fair coin

#### 6.1 mean

The expected value or mean of a binomial distribution.

```{r}
bin_mean(4,0.5)
```

#### 6.2 variance

The variance of a binomial distribution 

```{r}
bin_variance(4, 0.5)
```

#### 6.3 mode

The most likely number of a binomial distribution

```{r}
bin_mode(4, 0.5)
```


#### 6.4 skewness

Skewness is a measure of the asymmetry of the probability distribution of a random variable about its mean. 

```{r}
bin_skewness(4, 0.5)
```

#### 6.5 kurtosis

The Kurtosis is a measure of the "tailedness" of the probability distribution of a random variable.

```{r}
bin_kurtosis(4, 0.5)
```


